lab_notebook

### 2018-12-20 lab_notebook.Rmd
new script with updated projection data and updated ITQ/Turf implementation in most recent year 2016

reupdating upside data with new ITQ list
```{r}
#Load Data
#Upside data
projection_data <- readRDS("data/projection_data.rds")

@@

fishery_itq_simple <- fisheries_with_itq %>%
  select(assess_id_short,"iq", "itq", "ivq", "turf" )

@@

>>>>

reupdating upside data with new ITQ list

###JULIETTE: check why the fisheries recent only has FALSE for turfs and no TRUEs

```{r}
#Load Data
#Upside data
projection_data <- readRDS("data/projection_data.rds")

@@

fishery_itq_simple <- fisheries_with_itq %>%
  select(assess_id_short,iq, itq, ivq, turf )

@@

## adding turf information to upside projection (use fisheries recent?)
```{r}

turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")

turf_only <- turf_itq_isscaap %>%
  select(SciName, Country, turf)

fisheries_recent_generousturf_1 <- select(fisheries_recent, Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)

fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")

fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"

fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    ))

turfs <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "1")
no_itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "0")

sum(turfs$Catch, na.rm = TRUE)

sum(itq$Catch, na.rm = TRUE)

sum(no_itq$Catch, na.rm = TRUE)

turf only = 413 rows
fisheries recent = 5294

5643 actual rows
5707 when manually added added
- this means 64 species were matched with existing species in database
- when separated out all by species it was worse

- separate remaining by genus?

12/20/2018
new UN GDP data, 2016 only
Scaled GDPs
Rerun Regressions
###itq or turf: probablity of itq = f(ISSCAPP and GDP)
*regression converges*
```{r}

turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")

turf_only <- turf_itq_isscaap %>%
  select(SciName, Country, turf, SpeciesCat) %>%
  filter(SpeciesCat != 91) %>%
  filter(SpeciesCat != 92)

fisheries_recent_generousturf_1 <- fisheries_recent %>%
  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)%>%
  filter(SpeciesCat.x != 91) %>%
  filter(SpeciesCat.x != 92)

fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")

fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"

fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE | iq == FALSE | ivq == FALSE ~ "0"
    ))

gdp_all <- read_excel("data/un_gdp_2016.xls")

gdp <- gdp_all %>%
  select(Country, gdp_center) %>%
  filter( gdp_center != "NA")

join_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))

gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
gdp_rightsbased$rightsbased <- as.numeric(gdp_rightsbased$rightsbased)

itq_glm <- glm(formula = rightsbased ~ gdp_center + SpeciesCat, family = "binomial", data = gdp_rightsbased)
itq_glm

Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one

```{r}
fisheries_recent <- read_csv("data/fisheries_recent.csv")

turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")

turf_only <- turf_itq_isscaap %>%
  select(SciName, Country, turf, SpeciesCat) %>%
  filter(SpeciesCat != 91) %>%
  filter(SpeciesCat != 92)

fisheries_recent_generousturf_1 <- fisheries_recent %>%
  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)%>%
  filter(SpeciesCat.x != 91) %>%
  filter(SpeciesCat.x != 92)

fisheries_recent_generousturf <- merge(turf_only, fisheries_recent_generousturf_1, by = c("Country", "SciName"), all = "TRUE")

fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"

fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "1",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "0"
    ))

gdp_all <- read_excel("data/un_gdp_2016.xls")

gdp <- gdp_all %>%
  select(Country, gdp_center) %>%
  filter( gdp_center != "NA")

join_gdp_rightsbased <- merge(gdp, fisheries_recent_generousturf_rightsbased, by = c("Country"))

gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
gdp_rightsbased$rightsbased <- as.numeric(gdp_rightsbased$rightsbased)

itq_turf_glm <- glm(formula = rightsbased ~ gdp_center + SpeciesCat, family = "binomial", data = gdp_rightsbased)
itq_glm

summary(itq_turf_glm)
